---
title: "SFA_Pipeline_Paper"
author: "Sean Lam"
date: "2025-10-20"
output: html_document
---

```{r setup}
library(dplyr)
library(tidyr) 
library(tidyverse)
library(stringr)
library(lubridate)
library(readxl)
library(ggplot2)
library(scales)
library(plm)
library(frontier)
library(officer)
library(flextable)
library(corrplot)
library(MASS)
library(data.table)
library(purrr)
```
```{r}

```

```{r}
output_data_path <- "E:/Local_Dropbox/NUS Dropbox/Shao Wei, Sean Lam/Global Surgery-WS4/5. Hospital Level Study/Wrangling/Sean_Cleaned/Output"

other_data_path <- "E:/Local_Dropbox/NUS Dropbox/Shao Wei, Sean Lam/Global Surgery-WS4/5. Hospital Level Study/Raw_Data"
df_data <- read.csv(file.path(other_data_path, "Stage2_inst_data.csv"))

selected_inst <- c('HCTM', 'RIMS', 'SGH', 'ULin', 'UMMC', 'GNRC', 'FJMU','USU')
colnames(df_data) <- sub("^ï..", "", colnames(df_data))
df_data <- df_data[df_data$Institution %in% selected_inst, ]
```

1. Add 1 to any 0 values in the inputs following Battese (1997)

```{r}
columns_to_adjust <- c("COVID.beds.in.Use", "DoctorCOVIDDeployed", 
                       "NurseCOVIDDeployed", "EmergencyVolume", 
                       "ElectiveVolume")
df_data %>%
  summarise(across(all_of(columns_to_adjust), list(mean = ~mean(.x, na.rm = TRUE), 
                                           sd = ~sd(.x, na.rm = TRUE),
                                           median = ~median(.x, na.rm = TRUE),
                                           min = ~min(.x, na.rm = TRUE),
                                           max = ~max(.x, na.rm = TRUE))))

for(col in columns_to_adjust) {
  df_data[[col]] <- ifelse(df_data[[col]] == 0, 1, df_data[[col]])
}

df_data %>%
  summarise(across(all_of(columns_to_adjust), list(mean = ~mean(.x, na.rm = TRUE), 
                                           sd = ~sd(.x, na.rm = TRUE),
                                           median = ~median(.x, na.rm = TRUE),
                                           min = ~min(.x, na.rm = TRUE),
                                           max = ~max(.x, na.rm = TRUE))))

```

2. Normalize variables

```{r}
df_data$NormCOVIDBedsUse <- df_data$COVID.beds.in.Use / df_data$Bed.capacity

df_data$NormDoctorCOVIDDeployed <- df_data$DoctorCOVIDDeployed / df_data$Bed.capacity
df_data$NormNurseCOVIDDeployed <- df_data$NurseCOVIDDeployed / df_data$Bed.capacity
df_data$NormClinCOVIDDeployed <- (df_data$NurseCOVIDDeployed+df_data$DoctorCOVIDDeployed) / df_data$Bed.capacity

df_data$NormEmergencyVolume <- df_data$EmergencyVolume / df_data$Bed.capacity
df_data$NormElectiveVolume <- df_data$ElectiveVolume / df_data$Bed.capacity
df_data$NormSurgVolume <- (df_data$ElectiveVolume+df_data$EmergencyVolume) / df_data$Bed.capacity

```


3. Derive Cumulative and Marginal Responses

```{r}
df_data <- df_data %>%
  group_by(Institution) %>%
  arrange(Month) %>%  
  mutate(cum_admissions = cumsum(COVID_admissions),
         cum_deaths = cumsum(COVID_deaths)) %>%
  ungroup()

df_data$Cumulative.Response <- ifelse(df_data$cum_admissions != 0, 
                                      1 - df_data$cum_deaths / df_data$cum_admissions, 
                                      1)

df_data$Marginal.Response <- ifelse(df_data$COVID_admissions != 0, 
                                    1 - df_data$COVID_deaths / df_data$COVID_admissions, 
                                    1)

```


4. Bring in Response Indexes

```{r RI Wrangling}
ri_path <- "E:/Local_Dropbox/NUS Dropbox/Shao Wei, Sean Lam/Global Surgery-WS4/9. COVID Measure Cutoff Study/Pipeline/11. Results"

df_ri <- read.csv(file.path(ri_path,"selected_HRI_CRI.csv"))

cols_to_pivot <- c('C5_Close_public_transport', 'C6_Stay_at_home_requirements', 'C7_Restrictions_on_internal_movement',                    'C8_International.travel.controls', 'H1_Public.information.campaigns', 'H2_Testing.policy_x', 
                   'H3_Contact.tracing', 'H8_Protection.of.elderly.people', 'C3_Restrictions.on.visiting', 
                   'C4_Restrictions.on.internal.movement', 'C5_Perimeter.screening', 'C6_Active.screening', 
                   'C7_Visitor.controls', 'M1_Disposition', 'M2_Manpower.vaccination.rates..1.dose.', 
                   'M3_Manpower.vaccination.rates..2.doses.', 'M4_Workplace.closing', 'H1_Routine.instructions', 
                   'H2_Testing.policy_y', 'H3_Temperature.monitoring', 'H4_Splitting.surgical.teams', 
                   'H5_Surgery.Postponement', 'H6_Personal.Protective.Equipment.requirements')

df_ri_long <- reshape2::melt(df_ri, id.vars = c('Name', 'Date', 'Year.Month'), 
                   measure.vars = cols_to_pivot, 
                   variable.name = 'Policy', 
                   value.name = 'Value')
```

5. Set up the versions of REsponse Indexes

```{r}
########################
# Original Set
########################
# hgp_3 <- c('M1_Disposition', 'M2_Manpower.vaccination.rates..1.dose.', 'M3_Manpower.vaccination.rates..2.doses.', 'M4_Workplace.closing')
# hgp_4 <- c('H1_Routine.instructions', 'H2_Testing.policy_y', 'H3_Temperature.monitoring')
# hgp_5 <- c('H4_Splitting.surgical.teams', 'H5_Surgery.Postponement', 'H6_Personal.Protective.Equipment.requirements')

########################
# Version 6
########################
# Combined hgp_1 and hgp_2 - crowd control policies
hgp_1_2 <- c('C3_Restrictions.on.visiting', 'C4_Restrictions.on.internal.movement', 'C7_Visitor.controls', 'C5_Perimeter.screening', 'C6_Active.screening')
hgp_3 <- c('M4_Workplace.closing')
hgp_4 <- c('H1_Routine.instructions', 'H3_Temperature.monitoring', 'H6_Personal.Protective.Equipment.requirements')
hgp_5 <- c('H4_Splitting.surgical.teams', 'H5_Surgery.Postponement' )
hgp_6 <- c('M3_Manpower.vaccination.rates..2.doses.')

# Define cgp vector
cgp <- c('C5_Close_public_transport', 'C6_Stay_at_home_requirements', 'C7_Restrictions_on_internal_movement', 'C8_International.travel.controls', 'H1_Public.information.campaigns', 'H2_Testing.policy_x',
                   'H3_Contact.tracing', 'H8_Protection.of.elderly.people')
# cgp_1<-c('C5_Close_public_transport', 'C6_Stay_at_home_requirements', 'C7_Restrictions_on_internal_movement','C8_International.travel.controls')
# cgp_2<-c('H1_Public.information.campaigns','H2_Testing.policy_x', 
#                    'H3_Contact.tracing', 'H8_Protection.of.elderly.people')

label_policy <- function(policy) {
  if (policy %in% hgp_1_2) {
    return('HRI.1') # GP1n2
  } else if (policy %in% hgp_3) {
    return('HRI.2') #GP3
  } else if (policy %in% hgp_4) {
    return('HRI.3') #GP4
  } else if (policy %in% hgp_5) {
    return('HRI.4') #GP5
  } else if (policy %in% hgp_6) {
    return('HRI.5') #GP5
  } else if (policy %in% cgp) {
    return('CRI.1')
  } else {
    return('Other')
  }
}

df_ri_long$Group <- factor(sapply(df_ri_long$Policy, label_policy))

year_mth_order <- c('Jan-20', 'Feb-20', 'Mar-20', 'Apr-20', 'May-20', 'Jun-20',
                    'Jul-20', 'Aug-20', 'Sep-20', 'Oct-20', 'Nov-20', 'Dec-20',
                    'Jan-21', 'Feb-21', 'Mar-21', 'Apr-21', 'May-21', 'Jun-21',
                    'Jul-21', 'Aug-21', 'Sep-21', 'Oct-21', 'Nov-21', 'Dec-21')

df_ri_long$Year.Month <- factor(df_ri_long$Year.Month, levels = year_mth_order, ordered = TRUE)
df_ri_long$Month.No <- as.integer(df_ri_long$Year.Month)

```


6. Add `10` to all Response Indexes to avoid log of `0`. This is by definition for Response Indexes to facilitate Cobb-Douglas implementation

```{r}
# Add a constant 10 to the RIs
df_ri_long$Value <- df_ri_long$Value + 10
max_ri <- max(df_ri_long$Value)
```

7. Derive summary statistics of RI indexes for Regression Model

```{r}
q1 <- function(x) { quantile(x, 0.25, na.rm = TRUE) }
q3 <- function(x) { quantile(x, 0.75, na.rm = TRUE) }

df_wide <- df_ri_long %>%
  group_by(Name, Date, Year.Month, Month.No, Group) %>%
  summarise(Mean = mean(Value, na.rm = TRUE),
            Median = median(Value, na.rm = TRUE),
            Min = min(Value, na.rm = TRUE),
            Max = max(Value, na.rm = TRUE),
            Q1 = q1(Value),
            Q3 = q3(Value)) %>%
  pivot_wider(names_from = Group, values_from = c(Mean, Median, Min, Max, Q1, Q3)) %>%
  ungroup()
```

8. Bring in National Efficiency as a potential `inefficiency` factor

```{r}
country_to_institutions <- list(
  "Pakistan" = c("FJMU"),  
  "India" = c("GNRC", "RIMS"),
  "Malaysia" = c("HCTM", "UMMC"),
  "Singapore" = c("SGH"),
  "Indonesia" = c("ULin", "USU")
)

NatEff_path <- "E:/Local_Dropbox/NUS Dropbox/Shao Wei, Sean Lam/Global Surgery-WS4/4. National Level Study/GY national level analysis/Updated national level study/SFA paper"
df_nateff <- read.csv(file.path(NatEff_path,"Stage 1 result_24mon_22Jan.csv"))
df_nateff <- dplyr::select(df_nateff, Country, Date, e.eff)

df_nateff$Date <- as.Date(df_nateff$Date, format = "%Y-%m-%d")
df_nateff <- df_nateff %>%
  arrange(Country, Date) %>%  # Sort by Country and then Date
  group_by(Country) %>%
  mutate(Month.No = row_number()) %>% 
  ungroup()

df_nateff <- df_nateff %>%
  mutate(Institution = map(Country, ~ country_to_institutions[[.x]] %||% NA_character_))%>%
  unnest(Institution)

df_nateff$Date <- NULL
unique(df_nateff$Country)

merged_df <- merge(df_wide, df_data, by.x = c("Name", "Month.No"), by.y = c("Institution", "Month"))

merged_df <- merge(merged_df, df_nateff, by.x = c("Name", "Month.No"), by.y = c("Institution", "Month.No"))

merged_df <- rename(merged_df, national_efficiency = e.eff)

var_set3 <- c("Name","Date","Month.No","national_efficiency",
              "Mean_CRI.1",
              "Mean_HRI.1","Mean_HRI.2","Mean_HRI.3", 
              "Mean_HRI.4","Mean_HRI.5",
              "Median_CRI.1",
              "Median_HRI.1","Median_HRI.2","Median_HRI.3", 
              "Median_HRI.4","Median_HRI.5",
              "NormCOVIDBedsUse","NormDoctorCOVIDDeployed","NormNurseCOVIDDeployed","NormClinCOVIDDeployed",
              "NormEmergencyVolume","NormElectiveVolume","NormSurgVolume","Cumulative.Response","Marginal.Response" )
colnames(merged_df)
df_panel_sel <- merged_df[,var_set3]
df_panel_sel$Date <- as.Date(df_panel_sel$Date, format="%Y-%m-%d")
rows_with_na <- df_panel_sel %>% filter_all(any_vars(is.na(.)))

df_panel_sel <- df_panel_sel[complete.cases(df_panel_sel), ]
```

9. Derive the Lagged Columns for the Cumulative Response

```{r}
df_panel_sel <- df_panel_sel %>%
  arrange(Name, Date) %>%  
  group_by(Name) %>%       
  mutate(Cumulative.Response.lagged_1 = shift(Cumulative.Response, type = "lead", n=1, fill = NA)) %>%       
  mutate(Cumulative.Response.lagged_2 = shift(Cumulative.Response, type = "lead", n=2, fill = NA)) %>% 
  mutate(Cumulative.Response.lagged_3 = shift(Cumulative.Response, type = "lead", n=3, fill = NA)) %>% 
  mutate(Marginal.Response.lagged_1 = shift(Marginal.Response, type = "lead", n=1, fill = NA)) %>%
  mutate(Marginal.Response.lagged_2 = shift(Marginal.Response, type = "lead", n=2, fill = NA)) %>%
  mutate(Marginal.Response.lagged_3 = shift(Marginal.Response, type = "lead", n=3, fill = NA)) 
df_panel_sel$Month.No <- as.integer(df_panel_sel$Month.No)

```

10. Visualize the RI summary indexes to understand the directions of effects

```{r}
df_panel_temp<-df_panel_sel[c("Name","Date","Month.No","Median_HRI.1","Median_HRI.2","Median_HRI.3", 
                                                "Median_HRI.4", "Median_HRI.5")]#
df_long_temp <- pivot_longer(df_panel_temp, cols = c("Median_HRI.1","Median_HRI.2","Median_HRI.3", 
                                                "Median_HRI.4", "Median_HRI.5"), 
                        names_to = "HRI_Type", values_to = "Median_HRI_Value")
ggplot(df_long_temp, aes(x = Month.No, y = Median_HRI_Value, color = HRI_Type)) +
  geom_line() + # or geom_point() depending on your preference for visualization
  facet_wrap(~Name, scales = "free_y") + # Use facet_grid if you prefer a different layout
  theme_minimal() +
  labs(title = "HRI Type Across Months for Each Name Category",
       x = "Month",
       y = "Median HRI Value",
       color = "HRI Type") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```

11. Derive the Moving Average of all the explanatory variables for 3 dataframes for MA 1,2,3

```{r}
library(zoo)
# df_panel_sel$Mean_CRI.1_BMA <- rollapply(df_panel_sel$Mean_CRI.1, 3, mean, partial = TRUE, align = 'right')

var_set_MA <- c("national_efficiency","Mean_CRI.1","Mean_HRI.1","Mean_HRI.2","Mean_HRI.3", 
              "Mean_HRI.4","Mean_HRI.5",
              "Median_CRI.1","Median_HRI.1","Median_HRI.2","Median_HRI.3", 
              "Median_HRI.4","Median_HRI.5",
              "NormCOVIDBedsUse","NormDoctorCOVIDDeployed","NormNurseCOVIDDeployed","NormClinCOVIDDeployed",
              "NormEmergencyVolume","NormElectiveVolume","NormSurgVolume")

apply_MA_rolling_mean <- function(df, var_set, window_size) {
  for (var in var_set) {
    if (var %in% names(df)) {
      df[[paste0("MA_", window_size, "_",var )]] <- rollapply(df[[var]], window_size, mean, partial = TRUE, align = 'right')
    } else {
      cat("Column", var, "not found in dataframe\n")
    }
  }
  return(df)
}

df_panel_sel <- apply_MA_rolling_mean(df_panel_sel, var_set_MA, 1)
df_panel_sel <- apply_MA_rolling_mean(df_panel_sel, var_set_MA, 2)
df_panel_sel <- apply_MA_rolling_mean(df_panel_sel, var_set_MA, 3)
columns_to_prefix <- c("national_efficiency", "Mean_CRI.1", "Mean_HRI.1", "Mean_HRI.2", "Mean_HRI.3", "Mean_HRI.4",
                       "Mean_HRI.5", "Median_CRI.1", "Median_HRI.1", "Median_HRI.2", "Median_HRI.3", "Median_HRI.4",
                       "Median_HRI.5", "NormCOVIDBedsUse", "NormDoctorCOVIDDeployed", "NormNurseCOVIDDeployed",
                       "NormClinCOVIDDeployed", "NormEmergencyVolume", "NormElectiveVolume", "NormSurgVolume")

new_column_names <- ifelse(names(df_panel_sel) %in% columns_to_prefix, paste0("MA_0_", names(df_panel_sel)), names(df_panel_sel))
names(df_panel_sel) <- new_column_names
names(df_panel_sel)[names(df_panel_sel) == "Cumulative.Response"] <- "Cumulative.Response.lagged_0"
names(df_panel_sel)[names(df_panel_sel) == "Marginal.Response"] <- "Marginal.Response.lagged_0"
names(df_panel_sel)
```

12. Take the log transform of all the inputs/outputs columns for elasticity predictors (excludes the inefficiency columns)

```{r}
columns_to_log <- c("Cumulative.Response.lagged_0","Cumulative.Response.lagged_1", 
                    "Cumulative.Response.lagged_2","Cumulative.Response.lagged_3", 
                    "Marginal.Response.lagged_0","Marginal.Response.lagged_1",
                    "Marginal.Response.lagged_2", "Marginal.Response.lagged_3")

prefixes <- c("MA_0_", "MA_1_", "MA_2_", "MA_3_")
base_vars <- c("national_efficiency", "Mean_CRI.1", "Mean_HRI.1",
                  "Mean_HRI.2", "Mean_HRI.3", "Mean_HRI.4","Mean_HRI.5",
                  "Median_CRI.1", "Median_HRI.1", "Median_HRI.2",
                  "Median_HRI.3", "Median_HRI.4", "Median_HRI.5","NormCOVIDBedsUse",
                  "NormDoctorCOVIDDeployed", "NormNurseCOVIDDeployed","NormClinCOVIDDeployed",
                  "NormEmergencyVolume", "NormElectiveVolume","NormSurgVolume")
for(prefix in prefixes) {
  new_columns <- paste0(prefix, base_vars)
  columns_to_log <- c(columns_to_log, new_columns)
}
columns_to_log
apply_log_transformation <- function(df, columns_to_log) {
  for(col in columns_to_log) {
    df[[paste0("log_", col)]] <- log(df[[col]] + 1e-9)
  }
  return(df)
}

df_panel_sel <- apply_log_transformation(df_panel_sel, columns_to_log)
names(df_panel_sel)
```

13. Setup the 64 different combinations of experiments. Response is MLE, gamma, categories for coefficients defined as:
0: No Significance; 1: Significant Positive; 2: Significant Negative; 3: Not included in model

| Factor         | L1       | L2       |L3 |L4 |
| -------------- | -------- | -------- | - | - |
| Statistics     | Mean     | Median   |   |   |
| MA             | 0        | 1        | 2 | 3 |
| Response Lag   | 0        | 1        | 2 | 3 |
| Response Type  | Cumulative| Marginal|   |   |
| Clinician Type | Combined | Separate |   |   |


```{r}
statistics_levels <- c("Mean", "Median")
ma_levels <- c(0, 1, 2, 3)
response_lag_levels <- c(0, 1, 2, 3)
clinician_type_levels <- c("Combined", "Separate")

full_factorial_design <- expand.grid(Statistics = statistics_levels,
                                     MA = ma_levels,
                                     ResponseLag = response_lag_levels,
                                     ClinicianType = clinician_type_levels)
```

```{r}
base_elas_pred_vars <- c("CRI.1", "HRI.1",
                  "HRI.2", "HRI.3", "HRI.4","HRI.5")
                  
base_ineff_vars_comb <- c("national_efficiency","NormCOVIDBedsUse",
                  "NormClinCOVIDDeployed",
                  "NormEmergencyVolume", "NormElectiveVolume")

base_ineff_vars_sep <- c("national_efficiency","NormCOVIDBedsUse",
                  "NormDoctorCOVIDDeployed", "NormNurseCOVIDDeployed",
                  "NormEmergencyVolume", "NormElectiveVolume")

# response_vars <- c("Cumulative.Response.lagged_0","Cumulative.Response.lagged_1", 
#                     "Cumulative.Response.lagged_2","Cumulative.Response.lagged_3", 
#                     "Marginal.Response.lagged_0","Marginal.Response.lagged_1",
#                     "Marginal.Response.lagged_2", "Marginal.Response.lagged_3")
```

```{r}
full_factorial_design <- full_factorial_design %>%
  rowwise() %>%
  mutate(elas_preds = list(paste0("log_MA_", MA, "_", Statistics, "_", base_elas_pred_vars)),
         ineff_preds = if_else(ClinicianType == "Combined", 
                               list(paste0("MA_", MA, "_", base_ineff_vars_comb)),
                               list(paste0("MA_", MA, "_", base_ineff_vars_sep))),
         response = paste0("Cumulative.Response.lagged_", ResponseLag))
```

# ```{r}
# full_factorial_design$response[1]
# full_factorial_design$elas_preds[[1]]
# full_factorial_design$ineff_preds[[1]]
# for (i in 1:min(nrow(full_factorial_design), 64)) { # Adjust the 5 to view more rows if needed
#   cat("\nRow", i, "\n")
#   cat("elas_preds:\n")
#   print(full_factorial_design$elas_preds[[i]])
#   cat("ineff_preds:\n")
#   print(full_factorial_design$ineff_preds[[i]])
#   cat("\n---------------------------------------\n")
# }
# ```


```{r}
full_factorial_design$MLL <- NA
full_factorial_design$gamma <- NA
full_factorial_design$Model <- vector("list", nrow(full_factorial_design))

pdata <- pdata.frame(df_panel_sel, index = c("Name","Month.No"))

for (i in 1:nrow(full_factorial_design)) {
  full_formula <- as.formula(paste(full_factorial_design$response[i], 
                                   "~", paste(full_factorial_design$elas_preds[[i]], collapse=" + "), 
                                   "|", paste(full_factorial_design$ineff_preds[[i]], collapse=" + ")))
  
  pdata_sel <- pdata[, c("Name", "Month.No", full_factorial_design$elas_preds[[i]], full_factorial_design$ineff_preds[[i]], full_factorial_design$response[i])]
  pdata_sel_clean <- na.omit(pdata_sel)
  sfa_model <- sfa(full_formula, data = pdata_sel_clean)
  
  full_factorial_design$MLL[i] <- sfa_model$mleLogl
  full_factorial_design$gamma[i] <-  sfa_model$mleParam[which(names(sfa_model$mleParam)=="gamma")]
  full_factorial_design$Model[[i]] <- sfa_model
}
# names(full_factorial_design)
# full_factorial_design$Model[[1]]$mleParam 
# names(full_factorial_design$Model[[1]])
# summary(full_factorial_design$Model[[1]])
```



```{r}
mle_params_df <- data.frame(summary(full_factorial_design$Model[[2]],extraPar = TRUE)$mleParam)
mle_params_df
rownames_to_column(mle_params_df, var = "model.params")

str(summary(full_factorial_design$Model[[1]],extraPar = TRUE)$mleParam)
s <- summary(full_factorial_design$Model, extraPar = TRUE)
print(s)
str(sfa_model)
sfa_model$mleParam[which(names(sfa_model$mleParam)=="gamma")]^2
sfa_model$mleParam[which(names(sfa_model$mleParam)=="sigmaSq")]
sfa_model$mleParam
```


Key for var_columns: 0: No Significance; 1: Significant Positive; 2: Significant Negative; 3: Not included in model

1. Create columns for elasticity predictors

```{r}
for(var in base_elas_pred_vars) {
  full_factorial_design[[var]] <- NA
  full_factorial_design[[paste0(var, ".est")]] <- NA
  full_factorial_design[[paste0(var, ".p")]] <- NA
}

for(i in 1:nrow(full_factorial_design)) {
  temp_df <- data.frame(summary(full_factorial_design$Model[[i]])$mleParam)
  temp_df <- rownames_to_column(temp_df, var = "model.params")
  
  for(var in base_elas_pred_vars) {
    matching_rows <- which(grepl(var, temp_df$model.params))
  
    if(length(matching_rows) > 0) {
      estimate <- temp_df$Estimate[matching_rows[1]]
      pr_z <- temp_df$`Pr...z..`[matching_rows[1]]
 
      full_factorial_design[i, paste0(var, ".est")] <- estimate
      full_factorial_design[i, paste0(var, ".p")] <- pr_z

      ######### TEST 0.01 instead of 0.001 as significant [changed 5/5/2024]           
      if(estimate > 0 & pr_z < 0.01) {
        full_factorial_design[i, var] <- 1
      } else if(estimate < 0 & pr_z < 0.01) {
        full_factorial_design[i, var] <- 2
      } else if(pr_z >= 0.01) {
        full_factorial_design[i, var] <- 0
      } else {
        full_factorial_design[i, var] <- 99
      }
    } else {
      full_factorial_design[i, var] <- 3
    }
  }
}
```

2. Create columns for inefficiency predictors

```{r}
base_ineff_vars <- c("national_efficiency","NormCOVIDBedsUse",
                     "NormClinCOVIDDeployed",
                     "NormDoctorCOVIDDeployed", "NormNurseCOVIDDeployed",
                     "NormEmergencyVolume", "NormElectiveVolume")

for(var in base_ineff_vars) {
  full_factorial_design[[var]] <- NA
  full_factorial_design[[paste0(var, ".est")]] <- NA
  full_factorial_design[[paste0(var, ".p")]] <- NA
}

for(i in 1:nrow(full_factorial_design)) {
  temp_df <- data.frame(summary(full_factorial_design$Model[[i]])$mleParam)
  temp_df <- rownames_to_column(temp_df, var = "model.params")
  
  for(var in base_ineff_vars) {
    matching_rows <- which(grepl(var, temp_df$model.params))
  
    if(length(matching_rows) > 0) {
      estimate <- temp_df$Estimate[matching_rows[1]]
      pr_z <- temp_df$`Pr...z..`[matching_rows[1]]

      full_factorial_design[i, paste0(var, ".est")] <- estimate
      full_factorial_design[i, paste0(var, ".p")] <- pr_z

      ######### TEST 0.01 instead of 0.001 as significant [changed 5/5/2024]           

      if(estimate > 0 & pr_z < 0.01) {
        full_factorial_design[i, var] <- 1
      } else if(estimate < 0 & pr_z < 0.01) {
        full_factorial_design[i, var] <- 2
      } else if(pr_z >= 0.01) {
        full_factorial_design[i, var] <- 0
      } else {
        full_factorial_design[i, var] <- 99
      }
    } else {
      full_factorial_design[i, var] <- 3
    }
  }
}

categorical_columns <- c("CRI.1", "HRI.1", "HRI.2", "HRI.3", "HRI.4", "HRI.5",
                         "national_efficiency", "NormCOVIDBedsUse", "NormClinCOVIDDeployed",
                         "NormDoctorCOVIDDeployed", "NormNurseCOVIDDeployed",
                         "NormEmergencyVolume", "NormElectiveVolume")

```



```{r}
ggplot(full_factorial_design, aes(x = gamma, y = MLL)) +
  geom_point() + 
  theme_minimal() + 
  labs(x = "Gamma", y = "Maximum Likelihood (MLL)", 
       title = "Scatter Plot of MLL vs Gamma") 
```

```{r}
range(full_factorial_design$MLL)

min_value = 10
max_value = 300

ggplot(full_factorial_design, aes(x = MLL)) +
  geom_density(fill = "blue", alpha = 0.5) +
  labs(title = "Kernel Density Estimate of Maximum Loglikelihood for all Experiments",
       x = "MLL",
       y = "Density") +
  theme_minimal() +
  scale_x_continuous(limits = c(min_value, max_value))  


```


CLUSTERING MLL and GAMMA
```{r}
library(factoextra)
library(gridExtra)

data_for_clustering <- full_factorial_design[, c("MLL", "gamma")]
data_for_clustering_scaled <- scale(data_for_clustering)

set.seed(123) 
wss <- fviz_nbclust(data_for_clustering_scaled, kmeans, k.max = 12, method = "wss") + 
            ggtitle("") + theme( 
              plot.title = element_blank(),
              axis.title.x = element_text(size = 10),  
              axis.title.y = element_text(size = 10)  
              )
silhouette_values <- fviz_nbclust(data_for_clustering_scaled, kmeans, k.max = 12, method = "silhouette")+ 
            ggtitle("") + theme(
              plot.title = element_blank(),
              axis.title.x = element_text(size = 10),  
              axis.title.y = element_text(size = 10)  
              )
grid.arrange(wss, silhouette_values, nrow = 2)
```
```{r}
set.seed(6)
k3 <- kmeans(data_for_clustering_scaled, centers = 3)
full_factorial_design$cluster.MLL.gamma <- as.factor(k3$cluster)
# fviz_cluster(list(data = data_for_clustering_scaled, cluster = k3$cluster), geom = "point") +
#   ggtitle("k = 3")

fviz_cluster(list(data = data_for_clustering_scaled, cluster = k3$cluster), geom = "point",position = position_jitter(width = 0.2, height = 0.1), ellipse=FALSE) +
  scale_shape_manual(values = c(1, 2, 3)) +  
  scale_color_manual(values = c("black","black","black")) +
  labs(title = "K-means Clustering for Gamma and MLL", x = "Scaled MLL", y = "Scaled Gamma") +
  ggtitle("K-means Clustering for Gamma and MLL, k = 3") +
  theme_minimal() +
  theme(legend.position = "bottom") 

full_factorial_design_flat <- full_factorial_design %>%
  rowwise() %>%
  mutate(elas_preds = paste(unlist(elas_preds), collapse=", "),
         ineff_preds = paste(unlist(ineff_preds), collapse=", ")) %>%
  ungroup() %>%
  dplyr::select(-Model) 

```

RETAINING ONLY THE HIGH MLE CLUSTERS AND GAMMA <0.99 due to this 
**Warning: the parameter 'gamma' is close to the boundary of the parameter space [0,1]: this can cause convergence problems and can negatively affect the validity and reliability of statistical tests and might be caused by model misspecification**

```{r}
filtered_full_factorial_design <- subset(full_factorial_design, 
                                         (cluster.MLL.gamma == 2 | cluster.MLL.gamma == 3) & gamma <= 0.99)

key_labels <- setNames(c("no.sig", "sig.pos", "sig.neg", "not.inc", "NA"),
                       c("0", "1", "2", "3", "99"))

for (col in categorical_columns) {
  filtered_full_factorial_design[[col]] <- factor(filtered_full_factorial_design[[col]],
                                                  levels = names(key_labels),
                                                  labels = key_labels)
}
names(filtered_full_factorial_design)
```

```{r}
range(filtered_full_factorial_design$MLL)

gamma_plot <- ggplot(filtered_full_factorial_design, aes(x = gamma)) +
  geom_density(fill = "blue", alpha = 0.5) +
  labs(title = "Kernel Density Estimate of Gamma", x = "Gamma", y = "Kernel Density") +
  theme_minimal()
mll_plot <- ggplot(filtered_full_factorial_design, aes(x = MLL)) +
  geom_density(fill = "red", alpha = 0.5) +
  labs(title = "Kernel Density Estimate of MLL", x = "MLL", y = "Kernel Density") +
  theme_minimal()

grid.arrange(gamma_plot, mll_plot, ncol = 1)

```

```{r}

filtered_full_factorial_design$MLL_transformed <- rescale(filtered_full_factorial_design$MLL, to = c(3, 4), from = range(filtered_full_factorial_design$MLL, na.rm = TRUE))

MLL_min <- min(filtered_full_factorial_design$MLL, na.rm = TRUE)
MLL_max <- max(filtered_full_factorial_design$MLL, na.rm = TRUE)

ggplot(filtered_full_factorial_design, aes(x = gamma)) +
  geom_density(fill = "gray80", alpha = 1) +
  geom_point(aes(y = MLL_transformed, shape = as.factor(cluster.MLL.gamma)), 
             position = position_jitter(width = 0, height = 0.01),
             size=2, alpha = 0.5) + 
  scale_y_continuous(
    name = "Density",
    limits = c(0, 4),
    sec.axis = sec_axis(~ (. - 3) * (MLL_max - MLL_min) + MLL_min, name = "MLL")
  ) +
  scale_shape_manual(values=c(1, 4)) + 
  labs(shape = "Cluster") +
  labs(title = "Overlay of Gamma Density and MLL", x = "Gamma") +
  theme_minimal(base_size = 14)+
  theme(legend.position = "bottom") 

```

# PLOT DISTRIBUTION OF ESTIMATES FOR COVARIATES

```{r}
est_columns <- paste0(categorical_columns, ".est")
columns_to_include <- c("Statistics","MA","ResponseLag","ClinicianType",
                        "MLL", "gamma", est_columns, categorical_columns)
filtered_temp<-filtered_full_factorial_design[,columns_to_include]

plot_list <- list()

for (i in 1:length(est_columns)) {
  col_name <- est_columns[i]
  x_min <- min(filtered_temp[[col_name]], na.rm = TRUE) - (sd(filtered_temp[[col_name]], na.rm = TRUE) * 3)
  x_max <- max(filtered_temp[[col_name]], na.rm = TRUE) + (sd(filtered_temp[[col_name]], na.rm = TRUE) * 3)
  
  plot <- ggplot(filtered_temp, aes_string(x = col_name)) + 
          geom_density(fill = "blue", alpha = 0.5, na.rm=TRUE, adjust=5) +  # Using geom_density for density plots
          theme_minimal(base_size = 6) + 
          labs(title = col_name, x = NULL, y = "Density") +
          theme(axis.text.x = element_text(angle = 45, hjust = 1),
                plot.title = element_text(size = rel(1.2))) +
          xlim(x_min, x_max)
  plot_list[[i]] <- plot
}

do.call("grid.arrange", c(plot_list, ncol = 3, top = "Density of Estimates"))
```

# Summarize results for estimates and direction of effects

```{r}
kde_results_df <- data.frame(Name = character(),
                         mean = numeric(),
                         sd=numeric(),
                         stringsAsFactors = FALSE)
for (col_name in est_columns) {
  data_vector <- na.omit(filtered_temp[[col_name]])  # Remove NA values
  mean_value <- mean(data_vector)
  sd_value <- sd(data_vector)
  kde_results_df <- rbind(kde_results_df, data.frame(Name = col_name, 
                                             mean = mean_value, sd = sd_value))
}

list_of_freq_dfs <- list()
categorical_columns

for(col_name in categorical_columns) {
  freq_df <- filtered_temp %>%
    count(!!sym(col_name)) %>%
    rename(Category = !!sym(col_name), Count = n) %>%
    mutate(Name = col_name) %>%
    dplyr::select(Name, Category, Count)
  
  list_of_freq_dfs[[col_name]] <- freq_df
}
combined_freq_df <- bind_rows(list_of_freq_dfs)
combined_freq_df_wide <- pivot_wider(combined_freq_df, 
                        names_from = Category, 
                        values_from = Count,
                        values_fill = list(Count = 0)) 
combined_freq_df_wide <- combined_freq_df_wide %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)), na.rm = TRUE)) %>%
  ungroup()
kde_results_df$Name <- gsub(".est", "", kde_results_df$Name, fixed = TRUE)
merged_kde_freq_df <- left_join(kde_results_df, combined_freq_df_wide, by = "Name")

output_file_path <- file.path(output_data_path, "Filtered_Estimates.csv")
write.csv(merged_kde_freq_df, output_file_path)

```

```{r}
columns_to_include <- c("Statistics","MA","ResponseLag","ClinicianType",
                        "MLL", "gamma", categorical_columns)
filtered_temp<-filtered_full_factorial_design[,columns_to_include]

plot_list <- list()

for (i in 1:length(categorical_columns)) {
  col_name <- categorical_columns[i]
  plot <- ggplot(filtered_temp, aes_string(x = col_name)) + 
          geom_bar() + 
          theme_minimal(base_size=6) + 
          labs(title = col_name, x = NULL, y = "Count") +
          theme(axis.text.x = element_text(angle = 45, hjust = 1),
                plot.title = element_text(size = rel(1.2)))  
  plot_list[[i]] <- plot
}

do.call("grid.arrange", c(plot_list, ncol = 3, top = "Direction of Effects"))

```
# Analysis of lags in 36 runs

```{r}
ggplot(filtered_temp, aes(x=MA)) + 
  geom_histogram(binwidth = 0.5, fill="skyblue", color="black") + 
  theme_minimal() + 
  labs(title="Histogram of MA (Moving Average)", x="MA Values", y="Frequency")

ggplot(filtered_temp, aes(x=ResponseLag)) + 
  geom_histogram(binwidth = 1, fill="lightgreen", color="black") + 
  theme_minimal() + 
  labs(title="Histogram of ResponseLag", x="ResponseLag Values", y="Frequency")

```

```{r}
tables_list <- list()

for (col in names(filtered_temp)[c(7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19)]) {
  tab <- table(filtered_temp[[col]],useNA="no")
  df <- as.data.frame(tab)
  df$Variable <- col
  colnames(df)[1] <- "Level"
  colnames(df)[2] <- "Count"
  tables_list[[col]] <- df
}
filtered_summary_df <- bind_rows(tables_list)
filtered_summary_df <- pivot_wider(filtered_summary_df, names_from = Level, values_from = Count, id_cols = Variable) %>% dplyr::select (-"NA")


```


# (a) Cluster 3 (low gamma)

```{r}
columns_to_include <- c("Statistics","MA","ResponseLag","ClinicianType",
                        "MLL", "gamma", est_columns, categorical_columns)
filtered_temp_low <- filtered_full_factorial_design %>%
  filter(cluster.MLL.gamma == 3) %>%
  dplyr::select(all_of(columns_to_include))

for (i in 1:length(est_columns)) {
  col_name <- est_columns[i]
  x_min <- min(filtered_temp_low[[col_name]], na.rm = TRUE) - (sd(filtered_temp_low[[col_name]], na.rm = TRUE) * 3)
  x_max <- max(filtered_temp_low[[col_name]], na.rm = TRUE) + (sd(filtered_temp_low[[col_name]], na.rm = TRUE) * 3)
  
  plot <- ggplot(filtered_temp_low, aes_string(x = col_name)) + 
          geom_density(fill = "blue", alpha = 0.5, na.rm=TRUE, adjust=5) +  # Using geom_density for density plots
          theme_minimal(base_size = 6) + 
          labs(title = col_name, x = NULL, y = "Density") +
          theme(axis.text.x = element_text(angle = 45, hjust = 1),
                plot.title = element_text(size = rel(1.2))) +
          xlim(x_min, x_max)
  plot_list[[i]] <- plot
}

do.call("grid.arrange", c(plot_list, ncol = 3, top = "Density of Estimates (Low Gamma)"))

```

```{r}

kde_results_df <- data.frame(Name = character(),
                         mean = numeric(),
                         sd=numeric(),
                         stringsAsFactors = FALSE)
for (col_name in est_columns) {
  data_vector <- na.omit(filtered_temp_low[[col_name]])  # Remove NA values
  mean_value <- mean(data_vector)
  sd_value <- sd(data_vector)
  kde_results_df <- rbind(kde_results_df, data.frame(Name = col_name, 
                                             mean = mean_value, sd = sd_value))
}

list_of_freq_dfs <- list()

for(col_name in categorical_columns) {
  freq_df <- filtered_temp_low %>%
    count(!!sym(col_name)) %>%
    rename(Category = !!sym(col_name), Count = n) %>%
    mutate(Name = col_name) %>%
    dplyr::select(Name, Category, Count)
  
  list_of_freq_dfs[[col_name]] <- freq_df
}
combined_freq_df <- bind_rows(list_of_freq_dfs)
combined_freq_df_wide <- pivot_wider(combined_freq_df, 
                        names_from = Category, 
                        values_from = Count,
                        values_fill = list(Count = 0)) 
combined_freq_df_wide <- combined_freq_df_wide %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)), na.rm = TRUE)) %>%
  ungroup()
kde_results_df$Name <- gsub(".est", "", kde_results_df$Name, fixed = TRUE)
merged_kde_freq_df <- left_join(kde_results_df, combined_freq_df_wide, by = "Name")

output_file_path <- file.path(output_data_path, "Filtered_Estimates_Low_Gamma_20102025.csv")
write.csv(merged_kde_freq_df, output_file_path)
```



```{r}
plot_list <- list()

for (i in 1:length(categorical_columns)) {
  col_name <- categorical_columns[i]
  plot <- ggplot(filtered_temp_low, aes_string(x = col_name)) + 
          geom_bar() + 
          theme_minimal(base_size=6) + 
          labs(title = col_name, x = NULL, y = "Count") +
          theme(axis.text.x = element_text(angle = 45, hjust = 1),
                plot.title = element_text(size = rel(1.2)))  
  plot_list[[i]] <- plot
}

do.call("grid.arrange", c(plot_list, ncol = 3, top = "Direction of Effects(Low Gamma)"))
mean_gamma <- mean(filtered_temp_low$gamma, na.rm = TRUE)
gamma_summary <- with(filtered_temp_low, c(
  Min = min(gamma, na.rm = TRUE),
  "1st Quartile" = quantile(gamma, probs = 0.25, na.rm = TRUE),
  Median = median(gamma, na.rm = TRUE),
  Mean = mean(gamma, na.rm = TRUE),
  "3rd Quartile" = quantile(gamma, probs = 0.75, na.rm = TRUE),
  Max = max(gamma, na.rm = TRUE),
  SD = sd(gamma, na.rm = TRUE),
  Variance = var(gamma, na.rm = TRUE)
))

gamma_summary_df <- as.data.frame(gamma_summary)
names(gamma_summary_df) <- c("Value")
gamma_summary_df$Statistic <- row.names(gamma_summary_df)
rownames(gamma_summary_df) <- NULL
gamma_summary_df <- gamma_summary_df[c("Statistic", "Value")]

output_file_path <- file.path(output_data_path, "Gamma_summary_Low_Gamma_20102025.csv")
write.csv(gamma_summary_df, output_file_path)
```

## (b) Cluster 2 (high gamma)
```{r}
columns_to_include <- c("Statistics","MA","ResponseLag","ClinicianType",
                        "MLL", "gamma", est_columns, categorical_columns)
filtered_temp_high <- filtered_full_factorial_design %>%
  filter(cluster.MLL.gamma == 2) %>%
  dplyr::select(all_of(columns_to_include))

for (i in 1:length(est_columns)) {
  col_name <- est_columns[i]
  x_min <- min(filtered_temp_high[[col_name]], na.rm = TRUE) - (sd(filtered_temp_high[[col_name]], na.rm = TRUE) * 3)
  x_max <- max(filtered_temp_high[[col_name]], na.rm = TRUE) + (sd(filtered_temp_high[[col_name]], na.rm = TRUE) * 3)
  
  plot <- ggplot(filtered_temp_high, aes_string(x = col_name)) + 
          geom_density(fill = "blue", alpha = 0.5, na.rm=TRUE, adjust=5) +
          theme_minimal(base_size = 6) + 
          labs(title = col_name, x = NULL, y = "Density") +
          theme(axis.text.x = element_text(angle = 45, hjust = 1),
                plot.title = element_text(size = rel(1.2))) +
          xlim(x_min, x_max)
  plot_list[[i]] <- plot
}

do.call("grid.arrange", c(plot_list, ncol = 3, top = "Density of Estimates (High Gamma)"))
```

```{r}
plot_list <- list()

for (i in 1:length(categorical_columns)) {
  col_name <- categorical_columns[i]
  plot <- ggplot(filtered_temp_high, aes_string(x = col_name)) + 
          geom_bar() + 
          theme_minimal(base_size=6) + 
          labs(title = col_name, x = NULL, y = "Count") +
          theme(axis.text.x = element_text(angle = 45, hjust = 1),
                plot.title = element_text(size = rel(1.2)))  
  plot_list[[i]] <- plot
}

do.call("grid.arrange", c(plot_list, ncol = 3, top = "Direction of Effects(High Gamma)"))
mean_gamma <- mean(filtered_temp_high$gamma, na.rm = TRUE)
gamma_summary <- with(filtered_temp_high, c(
  Min = min(gamma, na.rm = TRUE),
  "1st Quartile" = quantile(gamma, probs = 0.25, na.rm = TRUE),
  Median = median(gamma, na.rm = TRUE),
  Mean = mean(gamma, na.rm = TRUE),
  "3rd Quartile" = quantile(gamma, probs = 0.75, na.rm = TRUE),
  Max = max(gamma, na.rm = TRUE),
  SD = sd(gamma, na.rm = TRUE),
  Variance = var(gamma, na.rm = TRUE)
))

gamma_summary_df <- as.data.frame(gamma_summary)
names(gamma_summary_df) <- c("Value")
gamma_summary_df$Statistic <- row.names(gamma_summary_df)
rownames(gamma_summary_df) <- NULL
gamma_summary_df <- gamma_summary_df[c("Statistic", "Value")]

output_file_path <- file.path(output_data_path, "Gamma_summary_High_Gamma_20102025.csv")
write.csv(gamma_summary_df, output_file_path)
```

```{r}
kde_results_df <- data.frame(Name = character(),
                         mean = numeric(),
                         sd=numeric(),
                         stringsAsFactors = FALSE)
for (col_name in est_columns) {
  data_vector <- na.omit(filtered_temp_high[[col_name]])  # Remove NA values
  mean_value <- mean(data_vector)
  sd_value <- sd(data_vector)
  kde_results_df <- rbind(kde_results_df, data.frame(Name = col_name, 
                                             mean = mean_value, sd = sd_value))
}

list_of_freq_dfs <- list()

for(col_name in categorical_columns) {
  freq_df <- filtered_temp_high %>%
    count(!!sym(col_name)) %>%
    rename(Category = !!sym(col_name), Count = n) %>%
    mutate(Name = col_name) %>%
    dplyr::select(Name, Category, Count)
  
  list_of_freq_dfs[[col_name]] <- freq_df
}
combined_freq_df <- bind_rows(list_of_freq_dfs)
combined_freq_df_wide <- pivot_wider(combined_freq_df, 
                        names_from = Category, 
                        values_from = Count,
                        values_fill = list(Count = 0)) 
combined_freq_df_wide <- combined_freq_df_wide %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)), na.rm = TRUE)) %>%
  ungroup()
kde_results_df$Name <- gsub(".est", "", kde_results_df$Name, fixed = TRUE)
merged_kde_freq_df <- left_join(kde_results_df, combined_freq_df_wide, by = "Name")

output_file_path <- file.path(output_data_path, "Filtered_Estimates_High_Gamma_20102025.csv")
write.csv(merged_kde_freq_df, output_file_path)
```

# Plot boxplot of gammas across low, high and all

```{r}
filtered_temp_high$Group <- "High"
filtered_temp_low$Group <- "Low"

combined_df <- bind_rows(filtered_temp_high, filtered_temp_low)
box_gamma <- ggplot(combined_df, aes(x = Group, y = gamma, fill = Group)) +
  geom_boxplot() +
  scale_fill_manual(values = c("High" = "gray80", "Low" = "gray50")) +
  labs(title = "Gamma Distribution Across Groups", x = "Group", y = "Gamma") +
  theme_minimal() +
  theme(legend.position = "none")  

box_mll <- ggplot(combined_df, aes(x = Group, y = MLL, fill = Group)) +
  geom_boxplot() +
  scale_fill_manual(values = c("High" = "gray80", "Low" = "gray50")) +
  labs(title = "MLL Distribution Across Groups", x = "Group", y = "Max Loglikelihood") +
  theme_minimal() +
  theme(legend.position = "none")  

grid.arrange(box_gamma, box_mll, ncol = 2)
```

# Extract the number of lags counted for each cluster

```{r}
contingency_table <- table(filtered_temp_high$MA, filtered_temp_high$ResponseLag)
fisher_result_high <- fisher.test(contingency_table)
fisher_result_high

contingency_table_margins <- addmargins(contingency_table)
contingency_df_counts <- as.data.frame.matrix(contingency_table_margins)
rownames(contingency_df_counts) <- paste("MA", rownames(contingency_df_counts))
colnames(contingency_df_counts) <- paste("ResponseLag", colnames(contingency_df_counts))

contingency_table_props <- prop.table(contingency_table)
contingency_table_props_margins <- addmargins(contingency_table_props)
contingency_df_props <- as.data.frame.matrix(contingency_table_props_margins)
rownames(contingency_df_props) <- paste("MA", rownames(contingency_df_props))
colnames(contingency_df_props) <- paste("ResponseLag", colnames(contingency_df_props))

combined_df <- rbind(contingency_df_counts, contingency_df_props)

output_file_path <- file.path(output_data_path, "Response_MA_lags_high_gamma.csv_20102025")
write.csv(combined_df, output_file_path)
```

```{r}
contingency_table <- table(filtered_temp_low$MA, filtered_temp_low$ResponseLag)
fisher_result_low <- fisher.test(contingency_table)
fisher_result_low

contingency_table_margins <- addmargins(contingency_table)
contingency_df_counts <- as.data.frame.matrix(contingency_table_margins)
rownames(contingency_df_counts) <- paste("MA", rownames(contingency_df_counts))
colnames(contingency_df_counts) <- paste("ResponseLag", colnames(contingency_df_counts))

contingency_table_props <- prop.table(contingency_table)
contingency_table_props_margins <- addmargins(contingency_table_props)
contingency_df_props <- as.data.frame.matrix(contingency_table_props_margins)
rownames(contingency_df_props) <- paste("MA", rownames(contingency_df_props))
colnames(contingency_df_props) <- paste("ResponseLag", colnames(contingency_df_props))

combined_df <- rbind(contingency_df_counts, contingency_df_props)

output_file_path <- file.path(output_data_path, "Response_MA_lags_low_gamma.csv_20102025")
write.csv(combined_df, output_file_path)
```

```{r}
contingency_table <- table(filtered_temp$MA, filtered_temp$ResponseLag)
fisher_result_all <- fisher.test(contingency_table)
fisher_result_all

contingency_table_margins <- addmargins(contingency_table)
contingency_df_counts <- as.data.frame.matrix(contingency_table_margins)
rownames(contingency_df_counts) <- paste("MA", rownames(contingency_df_counts))
colnames(contingency_df_counts) <- paste("ResponseLag", colnames(contingency_df_counts))

contingency_table_props <- prop.table(contingency_table)
contingency_table_props_margins <- addmargins(contingency_table_props)
contingency_df_props <- as.data.frame.matrix(contingency_table_props_margins)
rownames(contingency_df_props) <- paste("MA", rownames(contingency_df_props))
colnames(contingency_df_props) <- paste("ResponseLag", colnames(contingency_df_props))

combined_df <- rbind(contingency_df_counts, contingency_df_props)

output_file_path <- file.path(output_data_path, "Response_MA_lags_all_gamma_20102025.csv")
write.csv(combined_df, output_file_path)
```



# Extract efficiencies from each Model for all Institutions with good LR (36 runs) in a list

```{r}
all_df_long_reference <- data.frame()

for (i in 1:length(filtered_full_factorial_design$Model)) {
  df <- as.data.frame(efficiencies(filtered_full_factorial_design$Model[[i]]))
  df$Institution <- rownames(df)
  
  df_long <- pivot_longer(df, 
                          cols = -Institution, 
                          names_to = "Month", 
                          values_to = "Efficiency")
  
  ID_col <- paste("Experiment:", i,
                  "Statistics:", filtered_full_factorial_design$Statistics[[i]], 
                  "MA:", filtered_full_factorial_design$MA[[i]], 
                  "ResponseLag:", filtered_full_factorial_design$ResponseLag[[i]],
                  filtered_full_factorial_design$ClinicianType[[i]],
                  sep = ": ")
  
  df_long$Experiment.Run <- ID_col
  all_df_long_reference <- rbind(all_df_long_reference, df_long)
}

output_file_path <- file.path(output_data_path, "Efficiencies_goodLR_36runs_20102025.csv")
write.csv(all_df_long_reference, output_file_path)
```

```{r}
names(all_df_long_reference)
ggplot(all_df_long_reference, aes(x = Institution, y = Efficiency)) +
  geom_boxplot() +
  labs(x = "Institution", y = "Efficiency") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(all_df_long_reference, aes(x = Efficiency, fill = Institution)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~ Institution, scales = "free") +
  labs(x = "Efficiency", y = "Density") +
  theme_minimal()

```

```{r}

all_df_long_reference$Month <- factor(all_df_long_reference$Month, levels = 1:18, ordered = TRUE)

mean_efficiency <- all_df_long_reference %>%
  group_by(Institution, Month) %>%
  summarise(mean_Efficiency = mean(Efficiency))

last_points <- mean_efficiency %>%
  group_by(Institution) %>%
  filter(Institution %in% c("USU", "RIMS", "ULin", "GNRC")) %>%  
  filter(Month == max(Month)) %>%
  ungroup()

line_types <- c("solid", "dashed", "dotdash", "dotted", "longdash", "twodash", "dotdash", "dashed")

ggplot(mean_efficiency, aes(x = Month, y = mean_Efficiency, linetype = Institution, group = Institution)) +
  geom_line() +
  labs(x = "Month", y = "Mean Efficiency") +
  scale_linetype_manual(values = line_types) + 
  theme_minimal() +
  theme(legend.position = "bottom") +
  geom_text(data = last_points, aes(label = Institution, hjust = 1.1, vjust=1.4), check_overlap = TRUE) 

```




# Extract efficiencies from each Model for all Institutions for all runs in a list

```{r}
all_df_long <- data.frame()

for (i in 1:length(full_factorial_design$Model)) {
  df <- as.data.frame(efficiencies(full_factorial_design$Model[[i]]))
  df$Institution <- rownames(df)
  
  df_long <- pivot_longer(df, 
                          cols = -Institution, 
                          names_to = "Month", 
                          values_to = "Efficiency")
  
  ID_col <- paste("Experiment:", i,
                  "Statistics:", full_factorial_design$Statistics[[i]], 
                  "MA:", full_factorial_design$MA[[i]], 
                  "ResponseLag:", full_factorial_design$ResponseLag[[i]],
                  full_factorial_design$ClinicianType[[i]],
                  sep = ": ")
  
  df_long$Experiment.Run <- ID_col
  all_df_long <- rbind(all_df_long, df_long)
}

output_file_path <- file.path(output_data_path, "Efficiencies_all_64runs_20102025.csv")
write.csv(all_df_long, output_file_path)
```

